A User-Extensible and Adaptable Parser Architecture

### 2008-12-03 doc/sgai-2008-slides.tex
Improvements after meeting Carl.

\begin{frame}
    \timingnote{30 seconds}
    \titlepage{}
\end{frame}

@@

        \item [XXX] This requires a parser for Postfix log files.

@@

@@

        \item [Framework] The framework handles loading rules and providing
            services (XXX BETTER WORD\@?) to actions, e.g.\ data storage,
            inter-action communication, XXX ANOTHER EXAMPLE\@.  For each
            input log line, the framework tries each rule in turn until one
            matches, then it invokes the action specified by the rule.

@@

        \item Cascaded Parsing.  XXX SHOULD I HAVE A REFERENCE\@?

        \item The parser does not need to be recompiled when rules are
            changed, allowing: quicker testing of modified rules; different
            rulesets can easily be used; combining two or more rulesets.

        \item Rules can be changed or added by actions while the parser is
            running, allowing dynamically changing parsing, e.g.\ macros.
            This feature must be used with care.

        \item The architecture is capable of parsing inputs that are not
            completely understood, e.g.\ when developing a parser: the
            framework will warn about unparsed inputs but will continue on
            parsing as best it can.

        \item Parsing can optionally be stateful, e.g.\ parsing a
            programming language.

        \item XXX MORE FEATURES\@?

@@

        \item The architecture scales extremely well as the number of rules
            increases: a 46.05\% increase in Postfix ruleset resulted in a
            mean increase of 0.63\% in parsing time.

        \item Parsing time scales linearly with input size, but is affected
            by input content.

        \item 169 rules: the top 10\% match 85.03\% of log lines, the
            remainder tailing off similar to a Power Law distribution.

@@

        \item Use Machine Learning instead of writing rules; Instance Based
            Learning techniques a requirement due to the size of the data
            set.

        \item Detection of overlapping rules.

@@

\section*{Summary}

@@

        \item XXX MAYBE ON A SEPARATE SLIDE\@?

@@

        \item Suggestions?

>>>>

\begin{frame}
    \timingnote{30 seconds}
    \titlepage{}
    XXX EMAIL ADDRESSES\@.
\end{frame}

@@

        \item [Conclusion] This requires a parser for Postfix log files.

@@

    XXX SAMPLE LOG LINE\@; MAYBE HOW IT IS PARSED\@?

@@

        \item [Framework] The framework handles loading rules and providing
            support functions to actions, e.g.\ data storage, inter-action
            communication, and utility functions.  For each input log line,
            the framework tries each rule in turn until one matches, then
            it invokes the action specified by the rule.

@@

        \item The architecture is capable of parsing inputs that are not
            completely understood, e.g.\ when developing a parser: the
            framework will warn about unparsed inputs but will continue on
            parsing as best it can.  \timingnote{Emphasise this.}

        \item Rules can be tagged with conditions which must hold before
            the rule will be used to match an input.  XXX MAYBE EXTEND THIS
            A LITTLE WITH AN EXAMPLE\@?  DO I NEED AN EXAMPLE, WHEN THERE'S
            ONE IN A COUPLE OF SLIDE'S TIME\@?

        \item The parser does not need to be recompiled when rules are
            changed, allowing: quicker testing of modified rules; easing
            interchange of rulesets; combining two or more rulesets.

        \item Cascaded Parsing.

        \item Rules can be changed or added by actions while the parser is
            running, allowing dynamically changing parsing, e.g.\ macros.
            This feature must be used with care.  \timingnote{Currying
            functions in a calculator might be a good example.}

        \item 169 rules parsing 522 contiguous log files: the top 10\% of
            the rules match 85.03\% of the log lines, the remainder tailing
            off similar to a Power Law distribution.

        \item Most actions are triggered by one or two rules, because they
            deal with special cases.  Three actions are triggered by more
            than 40 rules.  \timingnote{build/stats-action-distribution}
            XXX EXPAND ON THIS\@?

@@

        \item The architecture scales extremely well as the number of rules
            increases: a 46.05\% increase in the Postfix ruleset ($115
            \rightarrow{} 169$ rules) resulted in a mean increase of 0.63\%
            in parsing time.

        \item Parsing time scales linearly with input size, but
            \textit{is\/} affected by input content.

@@

        \item Data mining to determine how well each anti-spam technique
            works.

        \item Data mining to search for combinations of features which can
            be used to detect spam, and development of new anti-spam
            techniques to defeat such spam.

        \item Use Machine Learning instead of writing rules; Instance Based
            Learning techniques a requirement due to the size of the data
            set.  \timingnote{Compare to SLCT-based tool.}

        \item Detection of overlapping rules.  XXX MORE DETAILS\@.

@@

\section{Summary}

@@

@@
